A Simple Minibatch Acceptance Test for MCMC

### 2016-05-18 nips_2016.tex
revise the algo

\begin{algorithm}[t]
\KwData{$\{x_i\}$ under a target distribution}
\KwResult{A series of sampled $\{\theta_i\}$ under the posterior distribution} 
set the $var(\Delta') = 1.0$ and deconvolve $X$ to get the distribution of $X_{corr}$\;
\While{not enough sampled data}{
	estimate the $sd(\Delta')$\;
    propose a candidate $\theta'$\;
    compute the noisy $\Delta'$\;
    sample a $x$ from $X_{corr}$\;
    \eIf{$x*sd(\Delta') + \Delta' > 0$}{
        Accept the $\theta'$;
    }{
        Reject the $\theta'$;
    }
}
\caption{A description of our MH test.}
\label{alg:our_algorithm}
\end{algorithm}

>>>>

\begin{algorithm}[t]
\KwData{$\{x_i\}$ under a target distribution}
\KwResult{A series of sampled $\{\theta_i\}$ under the posterior distribution} 
pre-compute the distribution of $X_{corr}$ under the different value of $var(\Delta')$\;
\While{not enough sampled data}{
	estimate the $sd(\Delta')$\;
	choose the distribution of $X_corr$ from the pre-computed distribution family\;
    propose a candidate $\theta'$\;
    compute the noisy $\Delta'$\;
    sample a $x$ from $X_{corr}$\;
    \eIf{$x + \Delta' > 0$}{
        Accept the $\theta'$;
    }{
        Reject the $\theta'$;
    }
}
\caption{A description of our MH test.}
\label{alg:our_algorithm}
\end{algorithm}
